### 2014-08-09 Docs/flowchart/flowchart.tex
more equationing

\subsection{Base State and Perturbation Form Equations}

The base state evolution equations for density and enthalpy can be
found by averaging (\ref{eq:flow:continuity}) and (\ref{eq:flow:enthalpy})
respectively over a layer of constant radius, resulting in
\begin{eqnarray}
\frac{\partial(\rho h)_0}{\partial t} &=& -\nabla\cdot\left[(\rho h)_0w_0\eb_r\right] +
  \psi + \overline{\rho \Hnuc} + \overline{\rho \Hext}. \label{eq:flow:enthalpy_base}
\end{eqnarray}

>>>>

The base state evolution equations for density and enthalpy can be
found by averaging Eq~\ref{eq:flow:enthalpy}
over a layer of constant radius, resulting in
\begin{eqnarray}
\frac{\partial(\rho h)_0}{\partial t} &=& -\nabla\cdot\left[(\rho h)_0w_0\eb_r\right] +
  \psi + \overline{\rho \Hnuc} + \overline{\rho \Hext}. \label{eq:flow:enthalpy_base}
\end{eqnarray}
Subtracting it from the full enthalpy equation gives:
\begin{equation}
\frac{\partial(\rho h)'}{\partial t} = -\Ub\cdot\nabla(\rho h)' - (\rho h)'\nabla\cdot\Ub - 
  \nabla\cdot\left[(\rho h)_0\Ubt\right] + \Ubt\cdot\nabla p_0 
   + ( \rho\Hnuc - \overline{\rho \Hnuc}) + (\rho\Hext - \overline{\rho \Hext}) 
\end{equation}
